\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
% \usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage[colorlinks=true,linkcolor=darkblue]{hyperref}
\usepackage{fontawesome}
\usepackage[margin=0.4in]{geometry}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{4.08003pt} % to supress package fancyhdr warning

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item[--]\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeItemWithHeader}[2]{
  \item[--]\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\awardsCustomItem}[2]{
  \item[--]
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    {\small#1} & \textit{\small#2} \\
  \end{tabular*}\vspace{-7.5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingSection}[2]{
  \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingWithDesc}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
    \vspace{-1pt}
    {\small #5}
    \vspace{-5pt}
}

\newcommand{\resumeSubItemNoHeader}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubItem}[2]{\resumeItemWithHeader{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------


\centerline{\textbf{{\LARGE Kha Vu Chan}}}\medskip
\centerline{
\faEnvelope \, \href{mailto:chankhavu@gmail.com}{chankhavu@gmail.com} \quad
\faLink \, \href{https://hav4ik.github.io/}{hav4ik.github.io} \quad
\faLinkedinSquare \, \href{https://www.linkedin.com/in/ha-vu-tran/}{ha-vu-tran} \quad
% \faStackOverflow \, \href{https://stackoverflow.com/users/4789373/}{FalconUA} \quad
\faGithub \, \href{https://github.com/hav4ik}{hav4ik}
}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Microsoft}{Seattle Area, WA}
      {Software Engineer --- Bing Image Search --- Core Relevance Team}{2019 --- Present}
      \resumeItemListStart
        \resumeItem{{\bf Accelerated} the training pipeline of the Bing Image {\bf Search Relevance Ranking} model by a {\bf 2x factor} and scaled it up, allowing more frequent shipment of relevance ranking models and enabling shorter experimentation iterations.}
        \resumeItem{Migrated the training pipeline of my team's Image Search Relevance Ranking model to AzureML platform. Improved the model development and experimentation process. Suggested design improvements to Azure \href{https://componentsdk.z22.web.core.windows.net/}{Component SDK} and \href{https://github.com/Azure/shrike}{Shrike}.}
        \resumeItem{From 2019 to 2021, worked in Excel. Created features to help users make more accessible docs. Worked on both back-end and client side for all supported platforms. Created a VSCode extension that makes the usage of internal tools easier.}
      \resumeItemListEnd

    \resumeSubheading
      {Samsung Research}{Kyiv, Ukraine}
      {Machine Learning Engineer --- Context Recognition Lab}{Feb 2017 --- Oct 2019}
      \resumeItemListStart
        \resumeItem
          {Optimized neural networks for mobile devices using pruning, quantization, representation sharing, distillation, weights sharing, and more. Achieved near-SOTA results with {\bf 50x improvement} in speed and memory usage.}
        \resumeItem
          {For 2 months, temporarily {\bf led a team} of 3 engineers for a Multi-Task Learning On-Device AI project. Drove the R\&D process, technical decisions, and overall direction of the project. Was responsible for the project's progress and results.}
        \resumeItem
          {Developed State-of-the-Art Deep Neural Networks for real-time Monocular 3D Scene Reconstruction of indoor scenes. Improved the stability of trained models by utilizing Tracking, SLAM, Object and Occlusion Detection techniques.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd



%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Taras Shevchenko National University of Kyiv}{Kyiv, Ukraine}
      {Master of Science in Applied Mathematics, specialized in Computational Mathematics.}
      {Sep 2017 -- Jun 2019}
      \resumeItemListStart
        \resumeItemWithHeader{MS thesis:}{Adaptive representation sharing in Multi-Task Networks. Developed a new greedy NAS method to find the optimal multi-task branching. Implemented other SOTA multi-objective gradient aggregation and NAS methods.}
      \resumeItemListEnd
    \resumeSubheadingSection
      {Bachelor of Science in Applied Mathematics, specialized in Computational Mathematics.}
      {Sep 2013 -- Jun 2017}
      \resumeItemListStart
        \resumeItemWithHeader{BS thesis:}{Breast Cancer Screening by analyzing the Interphase Nuclei of the Buccal Epithelium using Computer Vision techniques. Calibrated data to mitigate medical instrument biases. Developed an instance segmentation model.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Hydra -- a Deep Multi-Task Learning framework.}
      {Implemented SOTA Multi-Objective Optimization methods (e.g. GradNorm, MGDA-UB) and developed a new NAS method for Multi-Task Neural Nets.  (\href{https://github.com/hav4ik/Hydra}{github.com/hav4ik/Hydra})}
    \resumeSubItem{Eyesight -- a framework for Real-Time Computer Vision.}
      {A framework similar to \href{https://google.github.io/mediapipe/}{MediaPipe} for running real-time Computer Vision pipelines at the Edge. Supports Coral Edge TPU, RPi Camera, and more. (\href{https://github.com/hav4ik/eyesight}{github.com/hav4ik/eyesight})}
    \resumeSubItem{Google Landmarks Challenge 2020.}{In just 3 weeks (out of 2 months), created a large-scale deep metric learning, image retrieval, and re-ranking system. Created a novel training routine for ArcFace. Finished 22nd out of 736 teams ({\bf top 3\%}).}
  \resumeSubHeadingListEnd


%--------AWARDS AND HONORS-------------
\section{Awards and Honors}
  \resumeSubHeadingListStart
    \awardsCustomItem
      {All-Ukrainian Computer Science Competition by Minor Academy of Sciences ({\bf 3rd place} in 2012 and {\bf 3rd place} in 2013).}{}
    \awardsCustomItem
      {All-Ukrainian Intel ISEF Competition for high school students ({\bf 3rd place} in 2012 and {\bf 3rd place} in 2013).}{}
  \resumeSubHeadingListEnd


%--------TALKS, LECTURES, BLOG POSTS--------
\section{Miscellaneous}
  \resumeSubHeadingListStart
    \resumeSubItem{Deep Metric Learning lecturer}
      {(2021). Gave a lecture to Kyiv DS community. Live-stream: \href{https://youtu.be/aU9yEwgrJ54}{youtu.be/aU9yEwgrJ54}.}
    \resumeSubItem{\href{https://hav4ik.github.io/articles}{hav4ik.github.io/articles}}
      {--- personal blog where I write in-depth surveys \& posts related to math and deep learning.}
    \resumeSubItem{Competitive programming coach}
      {(2013 --- 2014). Prepared talented high-school students for National CS Olympiad.}
    
  \resumeSubHeadingListEnd

%-------------SKILLS-------------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{\bf Programming Languages:}
      {C/C++, Python, C\#, S\#, TypeScript, SQL, KustoQL, Bash, Java, JavaScript, MatLab.}
    \resumeSubItem{\bf Technologies \& Frameworks:}
      {PyTorch, TensorFlow, Keras, TF-Lite, OpenCV, scikit-learn, LightGBM, .NET, Django, Unreal Engine, QT, Android Programming, Caffe, AzureML, Apache Spark, Docker, Kubernetes, GCP, AWS.}
    \resumeSubItem{\bf Languages:}
      {English (TOEFL iBT 102), Vietnamese (native), Russian (native), Ukrainian (native).}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
